\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{orange}

\renewcommand*{\mobilephonesymbol}   {{\Large\faMobilePhone}~}
\renewcommand*{\emailsymbol}         {{\small\faInbox}~}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.85]{geometry}
\usepackage{fontawesome}

\name{André}{Silva Macedo}
\title{\normalfont 28 years old, Brazilian}
\address{\normalfont Belo Horizonte, Brazil}
\phone[mobile]{\normalfont +55~(31)~99838-5766}
\email{contato@andremacedo.dev}
\extrainfo{\normalfont\faGithub{ }\httplink{github.com/andreiox}}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2016--2019}{Bachelor degree}{FUMEC University}{Belo Horizonte - Brazil}{\textit{Computer Science}}{}

\section{About me}
\cvitem{}{
    A dedicated full-stack developer with 8 years of experience in software development.
    Polyglot programming skills in Java, Node.js, Python and, more recently, Clojure.
    Experience with software development of a new product, from the idea to the delivery.
    As well as experience in maintenance, refactoring and adding new functionality to an existing software.
}

\section{Experience}
\cventry{2022--present}{Senior Software Engineer}{Nubank}{}{}{
    Working with investments products and integrations with brazilian stock exchange B3 using exclusively Clojure-releated technologies.
}
\cventry{2020--2022}{Team Leader}{Seidor Véritas}{}{}{
    Leading the team responsible for the maintenance and evolution of tax documents issuance module (Outbound) from Orbit by Seidor platform.
}
\cventry{2019--2020}{Back-end Developer}{Seidor Véritas}{}{}{
    Designed and developed REST micro-services and AWS Lambdas using Node.js and Java 8.
    Development heavily focused in automated tests (unit and integration tests) and API documentation since the API is used by external clients;
    Responsible for the deploy of the whole infrastructure using Infrastructe as Code (aws-cdk).
    Infra composed by Elastic Beanstalk, ECS, Fargate, Lambda, API Gateway, and more.
}
\cventry{2018--2019}{Full-stack Developer}{Melhor Voo}{}{}{
    Developed various web pages and components using Node.js, React.js, Redux and JSS;
    Designed and implemented RESTful APIs using Express.js, Laravel and Django Rest Framework;
    Worked with MySQL and MongoDB databases;
    Developed web crawlers using Node.js and Python;
}
\cventry{2016--2018}{Full-stack Java Developer}{Registrocom.com}{}{}{
    Developed mostly web applications using Java 7, JSF 2.2 and 2, Primefaces 6 and 3, JPA (Hibernate and Eclipselink), MySQL and Apache Tomcat 8.
}

\section{Knowledge}
\cvitem{Frontend}{React, Primefaces, Flutter}
\cvitem{Backend}{Node.js, Java, Clojure, Python}
\cvitem{Frameworks}{Express, Fastify, Django, Flask, Spring Boot}
\cvitem{Databases}{MySQL, Postgres, MongoDB, DynamoDB, Datomic}
\cvitem{AWS}{Lambda, Step Functions, ECS, Fargate, EC2, Elastic Beanstalk, S3, API Gateway, Lambda Authorizers, RDS, Cognito, SQS, CodeBuild, CodePipeline, CDK (infra as code)}
\cvitem{Other}{Linux, Git, Scrum, Automated Tests}

\section{Languages}
\cvitemwithcomment{Portuguese}{Native}{}
\cvitemwithcomment{English}{Full professional proficiency}{}

\end{document}
